---
title: "IDA- Homework 1"
author: "986384 and 987144"
date: "November 14, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Task 1

## The data set I: Creating a table in RMarkdown

### Overview of variables in the data set


**Variable**  | __Variable Type__ | __Values__
:--------------:|:------------------:|:----------------------------------------------
brain regions | Nominal| Rostral middle frontal, Precentral, Lateral Occipital, Transverse Temporal, Temporal Pole |
surface area  | Metric |5941.8, 4718.8, 4672.9, 799.48, 443.3   |   
thickness     | Metric |2.59, 2.74, 2.3, 2.52, 3.66|
hemisphere    | Binary  |L,L,L,R,R|


# Task 2
## Loading relevant packages

```{r warning=FALSE, message=FALSE}
library(tidyverse)

```

# Task 3
## The data set II: Creating a tibble in R

```{r}
brain_data<- tibble(
  brain_regions = factor(c("Rostral middle frontal", "Precentral", "Lateral Occipital", "Transverse temporal", "Temporal pole")),
       surface_area = c(5941.8, 4718.8, 4672.9, 799.48, 443.3),
       thickness = c(2.59, 2.74, 2.3, 2.52, 3.66),
       hemisphere = c("L","L", 'L', 'R', 'R'))
brain_data

```

# Task 4

```{r}
library(purrr)
library(forcats)
brain_data$brain_regions <- fct_recode(brain_data$brain_regions, 
           "Banks Superior Temporal" = "Transverse temporal")
brain_data

```

# Task 5

```{r}
brain_data[2,3]
```

# Task 6

## The data set III: Creating a tibble in R

```{r}
brain_data2 <- brain_data
surface_area <- brain_data$surface_area
thickness <- brain_data$thickness
brain_data2 <- add_column(brain_data2, volume = surface_area*thickness)
brain_data2
```


# Task 7
 Why would it not work to use the same code to create a data frame instead of a tibble?
 Answer: The reason why using the same code would not work is that the operations done in above tasks are column based. Data Frame is a row based structure and does not allow such as changing the name of variable. Also, a data frame is not flexible to mathematical function when you try to apply it to the whole column. It might work with individual value in a certain row but not the complete column. 
 
 
# Miscellaneous: R basics
# Task 8

```{r}
regions_v1 <- brain_data2$brain_regions
regions_v1


```


# Task 9

```{r}
typeof(regions_v1)

```


# Task 10

```{r}
length(regions_v1)

```


# Task 11

Check again
```{r}

brain_data2$hemisphere %>% unique %>% length

```


# Task 12
Describe in no more than 10 words what the goal of this code is
Answer: Returns brain regions of the right hemisphere from brain_data2
```{r}
brain_data2[str_detect(brain_data2$hemisphere, "R"),"brain_regions"]

```


# Task 13

```{r}
x <- brain_data2$surface_area
y <- brain_data2$thickness

x
y

volume_calc <- function(x,y) {
  return(x*y)
}

volume_compare <- list(volume1 = brain_data2$volume, volume2 = volume_calc(x,y))
volume_compare

```


# Task 14

```{r}

volume_true <- as.numeric(c("17439","14351","12150","2386","2280.1"))
volume_true
volume_Calculated <- as.numeric(volume_compare$volume1)
volume_diff <- function(x,y) {
  return(x - y)
}


```


# Task 15

```{r}
brain_data3 <- tibble(
  regions = regions_v1,
  calculated_volume = volume_diff(volume_true, volume_Calculated)
)

brain_data3
```



# Task 16
Answer: This formula returns the value from column 1, which has the minimum calculated brain volume. 
Which brain region has the minimum calculated brain volume?
```{r}
brain_data3[which.min(brain_data3$calculated_volume),1]

```

# Task 17 

```{r}
family <- c("Gomez", "Morticia", "Pugsley", "Wednesday", "Uncle Fester", "Grandma")
map_chr(family, (function (x) {if (x != "Grandma" & x != "Uncle Fester") {str_c(x," Adams")} else {x}}))

```