---
title: "IDA HW 3"
author: 987144, 987154 And 986384
date: "November 26, 2019"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = F, message = F)
library(tidyverse)
library(dplyr)
```

#Exercise 1
## Reading & inspecting the data

```{r}

url_prefix <- "https://raw.githubusercontent.com/michael-franke/intro-data-analysis/master/data_sets/"
url_us  <- str_c(url_prefix, "YouTube-US.csv")
url_de  <- str_c(url_prefix, "YouTube-DE.csv")
url_cat <- str_c(url_prefix, "YouTube-categories.csv")


YouTube_data_US <- read.delim(url_us, header = T,sep = ",") 
YouTube_data_DE <- read.delim(url_de, sep = ",")
YouTube_data_categories <- read.delim(url_cat, sep = ";")

colnames(YouTube_data_DE)
```


## Pruning the data


```{r}
YouTube_data_US <- YouTube_data_US %>% select("title", "channel_title", "category_id", "tags", "views", "likes", "dislikes", "comment_count")

YouTube_data_DE <- YouTube_data_DE %>% select("title", "channel_title", "category_id", "tags", "views", "likes", "dislikes", "comment_count")

```


## Adding a column country

```{r}

YouTube_data_US <- YouTube_data_US %>% mutate(country = "US")
YouTube_data_DE <- YouTube_data_DE %>% mutate(country = "GER")

```



## Binding data sets

```{r}

YouTube_data_combined <-union(YouTube_data_US, YouTube_data_DE)
nrow(YouTube_data_combined)

```



## Joining Data Sets

```{r}

YouTube_data_full <- full_join(YouTube_data_combined, YouTube_data_categories, by = "category_id")

colnames(YouTube_data_full)

```



# Exercise 2

## Load the pre-processed YouTube data
```{r}
url_prefix <- "https://raw.githubusercontent.com/michael-franke/intro-data-analysis/master/data_sets/"
url_full  <- str_c(url_prefix, "YouTube-full.csv")

YouTube_data_full <- read.delim(url_full, sep = ",")
colnames(YouTube_data_full)
```

 
## Sorting by mean likes

```{r}
mean1 <- YouTube_data_full %>%
  group_by(category_name, country) %>%
  summarise(
    mean_likes = mean(likes)
  ) 


mean2 <- YouTube_data_full %>%
  group_by(category_name, country) %>%
  summarise(
    mean_dislikes = mean(dislikes)
  )
  
mean_final <- full_join(mean1, mean2)  
mean_final %>% 
  arrange(desc(mean_likes))
```



## Most viewed music video in Germany (4 points)

```{r}
Videos <- YouTube_data_full %>% 
  filter(category_name %in% "Music") %>%
  filter(country %in% "GER") %>%
  select(country, title, category_name, likes, views)
View(Videos)


```



## Counts of categories

```{r}
count <- YouTube_data_full %>%
  count(category_name)%>%
  arrange(n)

count$n <- as.numeric(count$n)

count %>%
  filter(n == median(count$n))

```



## Compare means and median

```{r}
YouTube_data_full %>%
  select(country, likes, dislikes, category_name) %>%
  group_by(country, category_name) %>%
  filter(category_name %in% c("Music", "Science & Technology")) %>%
  summarise(
    mean_likes = mean(likes),
    median_likes = median(likes)
  )

```

The reason for the significantly higher mean in the German music category may be that there are a few titles with a extremely high likes count which skewes the mean vs. the median to be higher.



# Exercise 3

## Code 1
```{r}
mode_of_factor <- function(vector){
  tx <- tibble(vector) %>% 
    dplyr::count(vector) %>%
      filter(n == max(n))
  return(tx$vector)
}
mode_of_factor(YouTube_data_full$category_name)

```

## Code 2 (Alternative)
```{r}

mode_of_factor1 <- function (vector) {
  vector %>% 
    enframe() %>%
    group_by(value) %>%
    summarise(
      count = n()
    ) %>%
    filter(count == max(count)) %>% pull(value)
  }

mode_of_factor1(YouTube_data_full$category_name)



```

# Exercise 4
```{r}
original <- c(1,2,3,4,5,2,2,6,12,7,4,5,7,3,2,1,5,6,8,5,10)
mean(original)
median(original)
added <- append(original, 32)
mean(added)
median(added)
  
```

# Exercise 5

$$\mu_\dot{x}=\frac{1}{n}\sum_{i=1}^n x_i$$


$$ Var(\vec{x})=\frac{1}{n}\sum_{i=1}^n(x_i-\mu_n)^2 $$








