---
title: "IDA HW 2"
author: 987144 and 986384
date: "November 19, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = F)
library(tidyverse)

```

# Task 1.a

```{r}

messy_data <- tribble(
  ~subject_id,  ~choices,  ~reaction_times,
  1,            "A,B,B",   "312 433 365",
  2,            "B,A,B",   "393 491 327",
  3,            "B,A,A",   "356 313 475",
  4,            "A,B,B",   "292 352 378"
)
messy_data$choices

```



```{r}

tidy1 <- messy_data %>%
  separate(
    col = choices,  
    into = str_c("C_", 1:3)
      )%>%
    pivot_longer(
      col = c(-reaction_times,-subject_id), 
      names_to = "conditions",
      values_to = "responses"
      )%>%
        select(subject_id, conditions, responses)
tidy1


tidy2 <- messy_data %>%
  separate(
    col = reaction_times,  
    into = str_c("C_", 1:3)
      )%>%
      pivot_longer(
        col = c(-choices,-subject_id), 
        names_to = "conditions",
        values_to = "RT"
        )%>%
          select(subject_id, conditions, RT)

tidy_data <- full_join(tidy1, tidy2, by = c("subject_id", "conditions"))
tidy_data$RT <- as.numeric(tidy_data$RT)
tidy_data
```               
   
#Task 1.b   
               
```{r}
tidy_data %>%
  group_by(conditions) %>%
  summarise(
    mean_RT = mean(RT)
  )

tidy_data %>%
  group_by(subject_id) %>%
  summarise(
    mean_RT = mean(RT),
    mean_RT = round(mean_RT, digits = 0)
  )



```
    
    
    
#Task 2.A
1) Is the “King of France” experiment an instance of a factorial design? If so, what is/are the factor(s), and what are the levels of each factor?
Answer: It is a factorial design. 5 Vignetes are teh five factors with 5 critical conditions to each of them.

2) Is this experiment a within-subjects or a between-subjects design?
Answer: Its a within subjects design as all the participants contribute to each factor.

3) Give one advantage and one disadvantage for this design-type (within- vs between-subjects).
Answer: Within Subjects advantage: no confound between conditions
        Within Subjects disadvantage: less association for analysis
        Between Subjects disadvantage: possible cross condition influence
        Between Subjects advantage: more association for analysis
                 
4) Is this experiment a repeated-measures design?
Answer: It is  not a repeated measure. Even though Each vignette has 5 critical sentences, exactly one from each condition is allocated completely at random for each Vignette.

5) Indicate the dependent variable of the experiment (give the column name in the data representation) and the corresponding variable type.
Answer: The dependent variable is the response and the varible type is boolean. 

  

#Task 2.B

```{r}
data_KoF_raw_IDA <- 
  read_csv(url('https://raw.githubusercontent.com/michael-franke/intro-data-analysis/master/data_sets/king-of-france_data_raw_IDA.csv'))
data_KoF_raw_IDA

###1

nrow(data_KoF_raw_IDA)

###2

data_KoF_raw_IDA %>%
  pull(submission_id) %>% unique %>% length

###3
data_KoF_raw_IDA %>%
  pull(comments) %>% unique %>% print

###4
data_KoF_raw_IDA %>%
  pull(languages) %>% unique %>% print

###5
   mean(data_KoF_raw_IDA$age, na.rm=TRUE)

###6
   
   summary(data_KoF_raw_IDA$age)

   
   
```
###7
submission_id: nominal

RT: metric

correct: boolean

education: ordinal

item_version:nominal

question:nominal

response:boolean

timeSpent:metric

trial_name: nominal

trial_number: nominal

trial_type: nominal

vignette: nominal



# Preprocessing of the Data
```{r}


data_KoF_processed <-  data_KoF_raw_IDA %>% 
  # discard practice trials
  filter(trial_type != "practice") %>% 
  mutate(
    # add a 'condition' variable
    condition = case_when(
      trial_type == "special" ~ "background check",
      trial_type == "main" ~ str_c("Condition ", item_version),
      TRUE ~ "filler"
    ) %>% 
      factor( 
        ordered = T,
        levels = c(str_c("Condition ", c(0, 1, 6, 9, 10)), "background check", "filler")
      )
  ) 

colnames(data_KoF_processed)

data_KoF_preprocessed_IDA <- data_KoF_processed %>%
  select(submission_id, trial_number, condition, vignette, question, correct,response)

data_KoF_preprocessed_IDA
```

Is the Data tidy?
The data_KoF_preprocesses_IDA is almost tidy as it fulfills the 2 conditions each variable forms a column and each observation forms a row. It is not completely tidy because it does not fulfill the last condition as questions and trial number column is not completely useful. 

#Towards Testing Hypotheses



```{r}
  
  data_KoF_preprocessed_IDA %>%
    filter(condition %in% c("Condition 0", "Condition 1")) %>%
      group_by(condition) %>%
        summarise(proportion_true = mean(response))
    




```




