---
title: "IDA HW 5 Group 66"
author: 987144, 987154 And 986384
date: "December 9, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Exercise 1

## Joint Probability

 **Table** | __Heads__ | __Tails__ |
:--------------:|:------------------:|:----------------------------------------------|
White |0.75 x 0.6 = 0.45|0.25 x 0.2 = 0.05 |
Black  |0.75 x 0.3 = 0.225 |0.25 x 0.5 = 0.125  |   
Red     | 0.75 x 0.1 = 0.075 |0.25 x 0.3 = 0.075|


## Marginal probability

$$ p(red ball) = 0.075 + 0.075 = 0.15 $$


## Conditional Probability 
$$  P(red | ¬black)=P(red | {red,white}) \\ Therefore \\ p(red | {red,white})= \frac{p(red \cap (red \cup white))}{p(red \cup white)} \\ We \ know \ A \cap(A \cup B) = A\ Therefore \\ = \frac{p(red)} {p(red \cup white)} \\ = \frac{0.15}{0.65} = 0.23 $$

## Bayes Rule

$$ p(Heads| Red\ Ball) = \frac{p(red ball | heads) * p(heads)}{p(red ball) \\ 
= \frac{0.075*0.75}{0.15} \\ = 0.375}  $$

# Exercise 2 

$$Given \ information \\ p(elevated\ blood\ gluscose) = 0.05,\\ p(notification|\  elevated\ blood\ glucose) = 0.995,\\p(notification|\ No\ elevation) = 0.02, \\ p(No\ elevated\ blood\ gluscose) = 0.95\\ p(elevated\ blood\ glucose|\ notification) = ?\\ = \frac{p(notification|\ elevated\ blood\ glucose) *p(elevated\ blood\ gluscose) }{p(notification)} $$


 **Table** | Calculation |
:--------------:|:------------------:|
p(notification given elevated) x p(elevation) |0.995 * 0.05 = 0.04975 |
p(notification given non elevated) x p(no elevation)  | 0.02 * 0.95 = 0.19 |  
Marginalized value for notification|0.06975|

$$ Substituting\ the \ values \\ = \frac{0.04975}{0.06975\\ = 0.713}$$



#Exercise 3

Probability of a desk being chooses, i.e., p(Desk) = 1/3. 
Probability of gold coin being chooses (probility of a drawers is opened with a gold coin), i.e, p(gold) = 3/6 = 1/2
Find p(GG| Sight Gold)
p(GG) = probability of desk have 2 gold coins in the 2 drawers
p(sight gold) = probility of a drawers is opened with a gold coin.

$$ p(GG|\ sight gold) = \frac{p(sight\ gold|\ GG)*p(GG)}{p(sight gold)} $$
p(sight gold| GG) means what is the probability of a drawer having gold given that the desk has gold coins in both drawers. We can surely say that the probability is 1. 

$$Therefore\ substituting\ the\ values\\ = \frac{1 * \frac{1}{3}}{\frac{1}{2}}\\ = \frac{2}{3} $$


# Exercise 4
## Let the critters roam

```{r}
n_critters <- 10000
critters_positions <- rep(0,n_critters)
n_steps <- 10000
for (i in 1:length(critters_positions)) {
  partial <- sum(runif(n = n_steps, min = -1, max = 1))
  critters_positions[i] <- partial
}
```

## Get summary statistics


```{r}
mean <- mean(critters_positions)
sd <- sd(critters_positions)  
mean 
sd
```

## Plot the critter positions


```{r}
n_samples <-  rnorm(critters_positions, mean = mean, sd = sd)


final <- tibble(source = rep('critters_positions'), x= critters_positions)
final2  <-   tibble(source = rep('n_samples'), x= n_samples)

final <-bind_rows(final, final2)

final%>%
  ggplot(aes(x, fill = source)) +
  geom_density(alpha = 0.5)

```

## Repeat for fewer samples
```{r}
n_critters <- 50
critters_positions <- rep(0,n_critters)

n_steps <- 10000
for (i in 1:length(critters_positions)) {
  partial <- sum(runif(n = n_steps, min = -1, max = 1))
  critters_positions[i] <- partial
}
mean <- mean(critters_positions)
sd <- sd(critters_positions)

n_samples <-  rnorm(10000, mean = mean, sd = sd)

final <- tibble(source = rep('critters_positions'), x= critters_positions)

final2  <-   tibble(source = rep('n_samples'), x= n_samples)
final <-bind_rows(final, final2)
final%>%
  ggplot(aes(x, fill = source)) +
  geom_density(alpha = 0.5)
```

## Interpret the critter walks

* rnorm creates a random value from the normal distribution based on the mean and standard. Whereas, runif generates a random value from the uniform distribution between two intervals.
* With rnorm, irrespective the sample size, it will still form a sample data which represents a normal distribution. 
* However, sample size does matter in critter walk/critter position, as more than a normal distribution it forms a uniform distribution.This means as the sample and minimum and maximum values changes the distribution also changes.
* Whereas,with rnorm even if the values change randomly and if you change the sample size the data will always represents a normal distribution.
* As you increase the sample size, the uniform distribution forms a more like a normal distribution.


# Homework 4 (Exercise 1)
## Smaller Vector
1) resampling the values of the vectors n times.
2) n times being 100
3) when you resample this values find the mean and the quantiles. 
4) Mean is the average. 
5) since we take a 95% interval. lower bound is 2.5%. Order the values in the ascending order. to find the position of the lower quantile we multiple the lower bound which is 0.025*(n+1). 
6) We do the same for the upper quantile just with the value 0.975. So, 0.975*(n+1)
7) We we calculate with the lower bound and we get 2.5 which we round of to 3. The 3rd position in the vector is nothing but 1.


```{r}

bootstrapped_CI <-  function(data_vector, n_resamples = 100) {
  resampled_means <- map_dbl(1:n_resamples, function(i) {
       mean(sample(x = data_vector, 
                   size = length(data_vector), 
                   replace = T)
       )
    }
  )
  tibble(
    'lower' = quantile(resampled_means, 0.025),
    'mean'  = mean(data_vector),
    'upper' = quantile(resampled_means, 0.975)
  ) 
}

d1 <- c(1,2,3)
bootstrapped_CI(d1)

```

## Larger vector

```{r}
d1 = c(1,2,3)
d2 = rep(d1,2)
d3 = rep(d1,10)

bootstrapped_CI <-  function(data_vector, n_resamples = 1e5) {
  resampled_means <- map_dbl(1:n_resamples, function(i) {
       mean(sample(x = data_vector, 
                   size = length(data_vector), 
                   replace = T)
       )
    }
  )
  tibble(
    'lower' = quantile(resampled_means, 0.025),
    'mean'  = mean(data_vector),
    'upper' = quantile(resampled_means, 0.975)
  ) 
}

bootstrapped_CI(d1)
bootstrapped_CI(d2)
bootstrapped_CI(d3)
```


## Effect of vector size

1) Vector size is inversely related to confidence score. 
2) Meaning, when the vector size is increasing, the confidence score between the quantile lower and mean and upper quantile and mean is decreasing. 
3) This happens because it decreases the standard error